\documentclass[12pt]{article}

\usepackage{dirtree}
\usepackage{hyperref}
\usepackage{amsmath}
\title{Notes for Julia Implementation of the Anderson-Moore Algorithm}
\author{Gary S. Anderson}
\begin{document}
\maketitle
\begin{description}
\item[Algorithm Resources] \ 
\begin{itemize}
\item \href{https://github.com/es335mathwiz/SPSolve.git}{SPSolve -- MATLAB implementation of the algorithm}
\item \href{https://github.com/es335mathwiz/sparseAMA.git}{sparseAMA -- ``C'' implementation of the algorithm}
\item \href{https://www.federalreserve.gov/econres/ama-index.htm}{FED's AMA site}
\item \href{https://www.sciencedirect.com/science/article/pii/S1474667017405064}{``A Reliable and Computationally Efficient Algorithm for Imposing the Saddle Point Property in Dynamic Models''}
\item \href{https://www.sciencedirect.com/science/article/pii/0165176585902113}{``A linear algebraic procedure for solving linear perfect foresight models''}
\end{itemize}
\item[Julia Resources] \
  \begin{itemize}
  \item \href{https://docs.julialang.org/en/stable/}{Documentation}
  \item \href{http://www.stochasticlifestyle.com/finalizing-julia-package-documentation-testing-coverage-publishing/}{Finalizing a Julia Package}
  \item \href{https://www.google.com/url?sa=t&rct=j&q=&esrc=s&source=web&cd=4&cad=rja&uact=8&ved=0ahUKEwjh_vH_h-DaAhUExYMKHYb7BWoQFgg5MAM&url=https%3A%2F%2Fgithub.com%2Ftonyhffong%2FLint.jl%2Fblob%2Fmaster%2Fdocs%2Ffeatures.md&usg=AOvVaw1FFQ9J64mhTjDx8QpQ-_zU}{Lint.jl}
  \end{itemize}

\item[Code] \
  
\dirtree{%
.1 AMAalg.
.2 exactShift.
.3 shiftRight.
.2 numericShift.
.3 shiftRight.
.2 buildA.
.2 eigenSystem.
.2 augmentQ.
.2 reducedForm.
}

\item[AMAalg] 

\item[exactShift]
\item[shiftRight]
\item[numericShift]
\item[shiftRight]
\item[buildA]
\item[eigenSystem]
\item[augmentQ]
\item[reducedForm]



\end{description}



\end{document}
